\documentclass[12pt]{article}
\usepackage{graphicx}
\graphicspath{ {./img/} }
\begin{document}
\section*{Agile}
\subsection*{Problems of heavy weight process}
\begin{itemize}
    \item The customer will put everything inside the requirement to not forget something
    \item As a result, most features are never used
    \item When the project is developed successfully, there is still a chance the demand has vanished
\end{itemize}
\subsection*{The agile manifesto}
Nothing new was invented in 2001. It was a "uncovering" of better ways of developing software.
The ideas were already there, just not commonly used.
\begin{itemize}
    \item Individuals and interactions over processes and tools
    \item Working software over comprehensive documentation
    \item Customer collaboration over contract negotiation
    \item Responding to change over following a plan
\end{itemize}
The 12 principles:
\begin{itemize}
    \item Satisfy the customer through early and continuous delivery
    \item Welcome changing requirements
    \item Deliver working software frequently
    \item Business people and developers must work together daily
    \item Trust the motivated individuals to get the job done
    \item The most efficient information exchange is face-to-face conversation
    \item Working software is the primary measure of progress
    \item Sustainable development at a steady pace (No overtime or stress)
    \item Continuous attention to technical excellence and good design enhances agility
    \item Simplicity (Maximize the amount of work not done)
    \item Best designs emerge from self-organizing teams
    \item At regular intervals the team reflects on how to become better.
\end{itemize}
\subsection*{eXtreme Programming (XP)}
Extreme Programming also contains some design and coding practices to develop agile software.
\subsubsection*{4 Variables}
\begin{itemize}
    \item Time
    \item Resources
    \item Quality
    \item Scope
\end{itemize}
External forces (customers, managers) can set the values for 3 of the variables.

The development team sets the value of the 4th one.

In agile projects: Quality needs to be high and fixed. Resources usually are fixed as well and time is limited so the scope is variable.
\subsubsection*{Cost of change}
Traditional view: cost of change increases with dev process of project.
XP view: cost of change should somewhat stay the same over time.
\subsubsection*{The values of XP}
See slides SoftEng Lecture 8 (25 - 35)
\subsubsection*{Practices}
See slides (35...)
\begin{itemize}
    \item Balance between business and technical considerations
    \item Business people decide about:
    \item Scope + Priority + Composition of releases + Dates of releases
    \item Technical people decide about:
    \item Estimates + Consequences + Process + Detailed Scheduling
\end{itemize}

\subsubsection*{Presentation}
\subsubsection*{Integration computer}


\end{document}